EWJN from a BCS Superconductor

### 2021-01-29 paper.tex
Adds more text about the cutoff and lack of cutoff in Lindhard case

However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
The divergence here stems from the unphysicality of local electrodynamics at very small scales;
within the electromagnetic coherence length of the metal the full response function defined by
\begin{equation}
	\vec{D}(\vec{r, t}) = \int \dd{r'} \dd{t'} \epsilon(r, r', t, t') \vec{E}(\vec{r', t'})
\end{equation}
becomes necessary.

We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so 
we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
\begin{align}
	r_p(u) &= \frac{\pi v - \zeta_p(u)}{\pi v + \zeta_p(u)} \\
	r_s(u) &= \frac{\zeta_s(u) - \frac{\pi}{v}}{\zeta_s(u) + \frac{\pi}{v}} \\
	\zeta_p(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\kappa^2} \left( \frac{y^2}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} + \frac{u^2}{\epsilon_(\frac{\omega}{c}\kappa, \omega)} \right) \label{eq:zp} \\
	\zeta_s(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} \label{eq:zs} \\
	\kappa^2 &= u^2 + y^2
\end{align}
The treatment in~\cite{QubitRelax} compares the difference between these expressions and the simpler Fresnel reflection coefficients.
In effect, using the Fresnel reflection coefficients for a metal for some constant conductivity corresponds to a local limit $u \rightarrow 0$.

@@

@@

This is the same divergence discussed in Langsjoen et al.~\cite{QubitRelax}, where for the normal state this problem does not arise if the Lindhard dielectric function is used.
Ultimately, this is because for $q > 2 q_{\mathrm{F}}$ the imaginary part of the Lindhard function goes to zero.
Physically, this happens because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart, which means there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.

>>>>

However, as discussed in~\cite{QubitRelax} and~\cite{Henkel2006}, this expression no longer remains accurate for arbitrarily small distances, with \eqref{eq:chi} diverging as $\frac{1}{z^3}$ as $z \rightarrow 0$.
The divergence here stems from the unphysicality of local electrodynamics at very small scales;
for $z$ smaller than the electromagnetic coherence length of the metal the full response function defined by
\begin{equation}
	\vec{D}(\vec{r, t}) = \int \dd{r'} \dd{t'} \epsilon(r, r', t, t') \vec{E}(\vec{r', t'})
\end{equation}
becomes necessary.
The experiment described by Kolkowitz et al.\cite{Kolkowitz2015} gives an example of a physical situation where the local description is insufficient, with a qubit probe at a distance from a silver film less than the film's mean free path.
Given that the coherence lengths of typical BCS superconductors can be larger than the distances used in that experiment, we should expect that the purely local description will not work for the superconducting case.

We can keep~\eqref{eq:chi} accurate for sufficiently small $z$ if we make appropriate changes to our reflection coefficients\cite{QubitRelax,Henkel2006}, so we use the reflection coefficients in Ford and Weber~\cite{Ford1984}:
\begin{align}
	r_p(u) &= \frac{\pi v - \zeta_p(u)}{\pi v + \zeta_p(u)} \\
	r_s(u) &= \frac{\zeta_s(u) - \frac{\pi}{v}}{\zeta_s(u) + \frac{\pi}{v}} \\
	\zeta_p(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\kappa^2} \left( \frac{y^2}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} + \frac{u^2}{\epsilon_(\frac{\omega}{c}\kappa, \omega)} \right) \label{eq:zp} \\
	\zeta_s(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} \label{eq:zs} \\
	\kappa^2 &= u^2 + y^2
\end{align}
The quantities $\zeta_p$ and $\zeta_s$ are proportional to the surface impedances of the metal, derived for this case by Ford and Weber\cite{Ford1984}, and with more thorough discussion in~\cite{LandauLifshitzElectrodynamics}.
The treatment in~\cite{QubitRelax} compares the difference between these expressions and the simpler Fresnel reflection coefficients.

@@

The Lindhard dielectric function reflects the important property of having an imaginary part that vanishes for $q$ such that $\abs{\varepsilon_q - \omega} >  q\vf$.
This is a very generic feature of these types of response functions, and occurs because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart.
Thus, there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
Because the Lindhard dielectric function's imaginary part vanishes above a cutoff $q_c\left(\omega\right)$ and has real part that goes as $\frac{1}{q^2}$, all of the integrals in $\eqref{eq:chi}, \eqref{eq:zp} and \eqref{eq:zs}$ converge.

@@

This is the same divergence discussed in Langsjoen et al.~\cite{QubitRelax}, where for the normal state this problem does not arise if the Lindhard dielectric function is used.
Ultimately, this is because for $q > 2 q_{\mathrm{F}}$ the imaginary part of the Lindhard function goes to zero.
